### 2010-03-08 papers/icfp-2010-desc/outline.tex
Desc@ICFP: more meat

\begin{structure}
<- Untyped lambda terms [figure]
    ???
\end{structure}

@@

\begin{structure}
<- Assuming a suitable notion of definitional equality for I
    ???
\end{structure}

\begin{structure}
<- Fin [figure]
    <- Presentation with equality constraints
    ???
\end{structure}

\begin{structure}
<- Vectors
    ???
\end{structure}

\begin{structure}
<- GADTS
    ???
\end{structure}

\begin{structure}
<- Brady optimization
    <- Source to source translation
    <- Able to remove some constraints
    -> Example: Fin [figure]
\end{structure}

@@

\begin{structure}
<- Untyped lambda terms
    ???
\end{structure}

\begin{structure}
<- IDesc
    ???
\end{structure}

>>>>

\begin{structure}
<- Untyped lambda terms [figure]
    <- Indexed by Nat
        <- De Bruijn "encoding"
    <- Variable in Fin n
        -> Correct by construction lambda term
    /> Lack the monadic structure [Altenkirch & Reus ???]
        -> Miss substitution operator
        /> Will be fixed later
\end{structure}

@@

\begin{structure}
!!! Need Help !!!
<- Assuming a suitable notion of definitional equality for I
    ???
\end{structure}

\begin{structure}
<- Fin [figure]
    <- Presentation with equality constraints
    <- Example of constrained constructor
        -> Constraints are translated into equalities
    ???
\end{structure}

\begin{structure}
<- Vectors
    Do we treat them in the end? 
    What can we say here we haven't with Fin?
\end{structure}

\begin{structure}
<- GADT-style data-type definition
    <- We directly support it
        <- Constraints turned into equalities
            <- Fin example
    <- Again, smooth transition from "today" data-types to advanced ones
        <- Same grammar
        /> More power
    /> Equations in data-types are not a blessing
        <- Complexify induction principle
        <- Lose match between data-type definition and the elimination form
\end{structure}

\begin{structure}
!!! Need Help !!!
<- Brady optimization: forcing
    <- Source to source translation
    <- Able to remove some constraints
    -> Example: Fin [figure]
    ??? More technical detail needed
\end{structure}

@@

\begin{structure}
<- Variation on a theme: free imonad construction
    <- Recall existence of generic free monad construction
    -> Present its generalization to IDesc [equation]
        <- \I -> IDesc I as describing an indexed endofunctor
        <- Free indexed monad construction
    -> Still a suitable, generic notion of substitution
        <- show type signature
        <- show implementation?? (space! space!)
\end{structure}

\begin{structure}
<- Untyped lambda terms
    <- Obvious instance of free monad
        <- Variable: Return
        <- App and Abst: indexed functor
        <- Bind: substitution
    -> Get a correct-by-construction lambda term
        /> With substitution for free!
        <- We should not pay for the structure which *is* here
\end{structure}

\begin{structure}
<- IDesc
    <- Another instance of free monad
        <- Var: Return
        <- Remaining: (not even indexed) functor
    -> Madness just starts
        <- map operation
        <- [ subst sigma D ] X = [D] (\x -> [subst sigma x] X)
        ???
\end{structure}
